A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
Add Opa to related work.

We are also not completely convinced that the ability to implicitly pass data
back and forth over the network is a unilaterally good thing; while this indeed
provides the programmer some extra convenience, it also requires the programmer
to exercise extra caution to avoid inadvertently sending large amounts of data
over the network.

@@

\paragraph{Ocsigen} Ocsigen\ \cite{ocsigen} enables the development of
client-server web applications using O'Caml. It accomplishes typed, seamless
communication by exposing mutable variables across the network. While this is a
quite flexible programming model, we believe that this uncontrolled, implicit
information flow makes programs harder to follow, debug, secure and optimize.

@@

>>>>

We are also not completely convinced that the ability to implicitly pass data
back and forth over the network is a unilaterally good thing; while this indeed
provides the programmer some extra convenience, it also requires the programmer
to exercise extra caution to avoid inadvertently sending large amounts of data
over the network or leak sensitive information.

\paragraph{Opa} The Opa framework\ \cite{opa}, much like Conductance, enables
seamless communication within the JavaScript language itself.
While Opa improves upon Conductance by introducing non-mandatory type checking
to the JavaScript world, its communication model is based on implicit
information flows, allowing the server to read and update mutable state on the
client and vice versa. While this is a quite flexible programming model, we
believe that this uncontrolled, implicit information flow makes programs harder
to follow, debug, secure and optimize.

@@

\paragraph{Ocsigen} Ocsigen\ \cite{ocsigen} enables the development of
client-server web applications using O'Caml. Much like Opa, it accomplishes
typed, seamless communication by exposing mutable variables across the network,
giving it many of the same drawbacks and benefits. While Ocsigen is a full
stack solution, denying the developer some flexibility in choosing their tools,
it should be noted that said stack is rather comprehensive and well tested.

@@

\bibitem[The Opa framework for JavaScript (2014)]{opa}
The Opa framework for JavaScript. Retrieved May 2, 2014, from http://opalang.org.
